---
title: "Retail Dashboard Summary Report"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
params:
  country: NULL
  data: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
library(ggplot2)
```

# Executive Summary

This report provides a dynamic summary of retail sales performance. It is generated based on your selections in the dashboard.

**Date generated:** `r Sys.Date()`  
**Country filter:** `r ifelse(is.null(params$country) || params$country == "", "All Countries", params$country)`

---

# Data Overview

```{r data-preview}
data <- params$data

if (is.null(data)) {
  stop("No data was passed to the report. Please check your dashboard filters.")
}

# Filter by selected country if provided
if (!is.null(params$country) && params$country != "") {
  data <- data %>% filter(Country == params$country)
}

# Show summary of the filtered data
summary(data)
```

---

# Sales Trends

```{r sales-trend-plot}
data %>%
  group_by(InvoiceDate) %>%
  summarize(TotalRevenue = sum(Revenue, na.rm = TRUE)) %>%
  ggplot(aes(x = InvoiceDate, y = TotalRevenue)) +
  geom_line(color = "steelblue") +
  labs(title = "Revenue Over Time", x = "Date", y = "Total Revenue") +
  theme_minimal()
```

---

# Top Selling Products

```{r top-products}
top_products <- data %>%
  group_by(Description) %>%
  summarize(QuantitySold = sum(Quantity)) %>%
  arrange(desc(QuantitySold)) %>%
  slice_max(QuantitySold, n = 10)

ggplot(top_products, aes(x = reorder(Description, QuantitySold), y = QuantitySold)) +
  geom_col(fill = "darkgreen") +
  coord_flip() +
  labs(title = "Top 10 Selling Products", x = "Product", y = "Quantity Sold") +
  theme_minimal()
```

---

# Customer Summary

```{r customer-insights}
customer_summary <- data %>%
  group_by(CustomerID) %>%
  summarize(TotalSpent = sum(Revenue), TotalOrders = n()) %>%
  arrange(desc(TotalSpent))

head(customer_summary, 10)
```

---

# Conclusion

This automatically generated report summarizes key retail KPIs based on your current dashboard view.

*Thank you for using the Retail Sales Dashboard.*
